analysis_stable

### 2020-08-14 inst/analysis/analysis_stable.Rmd
New dataset, expression size and so on

```{r eval_calls_file}
eval_calls_file <- "/var/lib/R/project-evalR/run/package-evals-traced-all.1/calls.fst"
```

@@

```{r expression_size}

eval_calls <- eval_calls %>% mutate(expr_expression_size = str_length(expr_expression), expr_resolved_size = str_length(expr_resolved), envir_expression_size = str_length(envir_expression), enclos_expression_size = str_length(enclos_expression))

```

```{r}
eval_calls %>% ggplot() +
  geom_histogram(aes(x = expr_expression_size), na.rm = TRUE, binwidth=1) +
  scale_x_log10() +  scale_y_sqrt()
```

If we remove the outliers:
```{r}
eval_calls %>% filter(expr_expression_size < 25000) %>% ggplot() +
  geom_histogram(aes(x = expr_expression_size), na.rm = TRUE, binwidth=2)  + scale_x_sqrt() +  scale_y_sqrt() 
```

@@

```{r code_size_srcref}
eval_calls %>% filter(is.na(eval_call_srcref), caller_package != "base") %>% ggplot() +
  geom_histogram(aes(x = expr_expression_size), na.rm = TRUE, binwidth=1) + scale_x_sqrt() + scale_y_sqrt()
```

And the average size per package:
```{r average_size_package}
eval_calls %>% group_by(caller_package) %>% summarize(average_expr_size = mean(expr_expression_size, na.rm = TRUE)) %>% arrange(desc(average_expr_size))
```

If we look at the maxima, the largest ones are in *base*:
```{r max_size_package}
eval_calls %>% group_by(caller_package) %>% summarize(max_expr_size = max(expr_expression_size, na.rm = TRUE)) %>% arrange(desc(max_expr_size))
```

@@

```{r eval_from_parse}
parsed_evals <- eval_calls %>% filter(!is.na(expr_parsed))
```

There are `r parsed_evals %>% nrow()` such calls, `r (parsed_evals %>% nrow()) / nb_eval_calls * 100`%.

@@

  We can differentiate further the provenance, i.e. whether the evaluated string comes from `file` or from `text`.

```{r parsed_evals_source}
parsed_evals <- parsed_evals %>% mutate(parse_args = map(expr_expression, function_arguments)) %>% unnest_wider(parse_args, names_repair = "unique")

```

>>>>

```{r eval_calls_file}
# All CRAN
#eval_calls_file <- "/var/lib/R/project-evalR/run/package-evals-traced-all.1/calls.fst"

# Subset (500 packages)
eval_calls_file <- "/var/lib/R/project-evalR/run/package-evals-traced-corpus.1/calls.fst"
```

@@

```{r}
eval_calls %>% ggplot() +
  geom_histogram(aes(x = expr_expression_length), na.rm = TRUE, binwidth=1) +
  scale_x_log10() +  scale_y_sqrt()
```

If we remove the outliers:
```{r}
eval_calls %>% filter(expr_expression_length < 25000) %>% ggplot() +
  geom_histogram(aes(x = expr_expression_length), na.rm = TRUE, binwidth=2)  + scale_x_sqrt() +  scale_y_sqrt() 
```

@@

```{r code_size_srcref}
eval_calls %>% filter(is.na(eval_call_srcref), caller_package != "base") %>% ggplot() +
  geom_histogram(aes(x = expr_expression_length), na.rm = TRUE, binwidth=1) + scale_x_sqrt() + scale_y_sqrt()
```

And the average size per package:
```{r average_size_package}
eval_calls %>% group_by(caller_package) %>% summarize(average_expr_size = mean(expr_expression_length, na.rm = TRUE)) %>% arrange(desc(average_expr_size))
```

If we look at the maxima, the largest ones are in *base*:
```{r max_size_package}
eval_calls %>% group_by(caller_package) %>% summarize(max_expr_size = max(expr_expression_length, na.rm = TRUE)) %>% arrange(desc(max_expr_size))
```

@@

```{r eval_from_parse}
parsed_evals <- eval_calls %>% filter(!is.na(expr_parsed_expression))
nb_parsed_evals <- parsed_evals %>% nrow()
```

There are `r nb_parsed_evals` such calls, `r nb_parsed_evals / nb_eval_calls * 100`%.

@@

  We can differentiate further the provenance, i.e. whether the evaluated string comes from `file` or from `text`. However, we can only do it for `parse`, `str2lang` and `str2expression` at the top level of `expr_expression`, not buried in a function call.

```{r parsed_evals_source}
parsed_evals_args <- parsed_evals %>% filter(str_detect(expr_parsed_expression, "(parse|str2lang|str2expression)\\(")) %>% mutate(parse_args = map(expr_parsed_expression, extract_args_parse)) %>% unnest_wider(parse_args,  names_sep = "_")
```

```{r}
nb_file <- parsed_evals_args %>% filter(!is.na(parse_args_file)) %>% nrow()
```

```{r}
nb_text <- parsed_evals_args %>% filter(!is.na(parse_args_text)) %>% nrow()
```

There are `r nb_file` calls with the `file` argument, and `r nb_text` with the `text` argument, i.e. `r  nb_file / nb_parsed_evals * 100`%, and `r nb_text / nb_parsed_evals *100`% respectively.
